---
title: "Latino"
output: html_document
---


Wrangling for Latino Census Tracts High Latino = 1
```{rsetup, include=FALSE}


library(tidyverse)
library(janitor)
#data_fe_carb_soc_latino<- data_fe_carb_soc %>% 
 # mutate(latino_bin = case_when(Percent_Hispanic <= 34 ~ "0", Percent_Hispanic >=34 ~ "1"))
  

#High and low latino tracts determined for 2014, carried throughout years of data

latino<- read_csv("merged_data_fe_carb_soc_latino.csv")

  
high_latino <- latino %>% 
  filter(latino_bin=="1")

low_latino <-latino %>% 
 filter(latino_bin=="0")

```


Fixed Effects on CARB-lm  All on 2014, 2015, 2016 with Latino Interactions
```{r}
  as.numeric(latino$latino_bin)

#Trying fixed effects with latino binary variables - Interaction term
carb_diabetes_latino <- lm(Diabetes ~ PM2.5 + (PM2.5*latino_bin) + factor(Census_Tract) + factor(Year) + Percent_Black_Only + Percent_American_Indian_and_Alaska_Native_Only + Percent_Hispanic + Education + Poverty + Unemployment, data = latino)

summary(carb_diabetes_latino)

#Trying fixed effects with two different latino equations
carb_diabetes_high_latino <- lm(Diabetes ~ PM2.5 + factor(Census_Tract) + factor(Year)+ Percent_Hispanic + Education + Poverty + Unemployment, data = high_latino)

summary(carb_diabetes_high_latino)

carb_diabetes_low_latino <- lm(Diabetes ~ PM2.5 + factor(Census_Tract) + factor(Year)+ Percent_Hispanic + Education + Poverty + Unemployment, data = low_latino)

summary(carb_diabetes_low_latino)


```


USING THE MEDIAN
-----------With latino interaction term

Call:
lm(formula = Diabetes ~ PM2.5 + (PM2.5 * latino_bin) + factor(Census_Tract) + 
    factor(Year) + Percent_Hispanic + Education + Poverty + Unemployment, 
    data = latino)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.52709 -0.15109  0.00009  0.16402  1.44620 

Coefficients: (1 not defined because of singularities)
                                 Estimate Std. Error t value Pr(>|t|)    
(Intercept)                     7.766e+00  2.049e-01  37.892  < 2e-16 ***
PM2.5                           .02078  6.817e-03   3.049 0.002305 ** 
latino_bin                      .005783  3.113e-01   1.858 0.063221 .  

*******Interaction term not significant

----------Keeping in black and Native seems to give a term that makes more sense 
Call:
lm(formula = Diabetes ~ PM2.5 + (PM2.5 * latino_bin) + factor(Census_Tract) + 
    factor(Year) + Percent_Black_Only + Percent_American_Indian_and_Alaska_Native_Only + 
    Percent_Hispanic + Education + Poverty + Unemployment, data = latino)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.51934 -0.15169  0.00042  0.16411  1.42410 

Coefficients: (1 not defined because of singularities)
                                                 Estimate Std. Error t value Pr(>|t|)    
(Intercept)                                     7.702e+00  2.047e-01  37.619  < 2e-16 ***
PM2.5                                           2.088e-02  6.804e-03   3.069 0.002150 ** 
latino_bin                                      3.458e-01  3.129e-01   1.105 0.269158 

--------------New equation With low hispanic areas only
Call:
lm(formula = Diabetes ~ PM2.5 + factor(Census_Tract) + factor(Year) + 
    Percent_Hispanic + Education + Poverty + Unemployment, data = low_latino)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.53198 -0.12962 -0.00123  0.13078  1.43267 

Coefficients:
                                 Estimate Std. Error t value Pr(>|t|)    
(Intercept)                     7.715e+00  1.784e-01  43.251  < 2e-16 ***
PM2.5                           .03197  6.693e-03   4.777 1.83e-06 ***


----------------New equation with high hispanic areas only
Call:
lm(formula = Diabetes ~ PM2.5 + factor(Census_Tract) + factor(Year) + 
    Percent_Hispanic + Education + Poverty + Unemployment, data = high_latino)

Residuals:
    Min      1Q  Median      3Q     Max 
-1.3802 -0.1796  0.0031  0.1929  1.4103 

Coefficients:
                                Estimate Std. Error t value Pr(>|t|)    
(Intercept)                     6.736947   0.265618  25.363  < 2e-16 ***
PM2.5                           0.022433   0.008358   2.684 0.007295 ** 
*********Coefficient not significant

SUMMMARY STATS - NOT FOR LATINO INTERACTION
```{r}


master<- read_csv("carb_ces_pm2.5_diabetes_ACSandCESsocio_race.csv") %>% 
  clean_names()

hist(master$percent_hispanic_or_latino_of_any_race_2014)
hist(master$percent_hispanic_or_latino_of_any_race_2015)
hist(master$percent_hispanic_or_latino_of_any_race_2016)

median(master$percent_hispanic_or_latino_of_any_race_2014, na.rm=TRUE)
median(master$percent_hispanic_or_latino_of_any_race_2015, na.rm=TRUE)
median(master$percent_hispanic_or_latino_of_any_race_2016, na.rm=TRUE)
#median is 33.1, 33.6, 33.7,
#call majority latino anything over 34%?


hist(carb_diabetes$pm_2014)
hist(carb_diabetes$pm_2015)
hist(carb_diabetes$pm_2016)
hist(carb_diabetes$pm_2017)
hist(carb_diabetes$pm_2017, breaks=32)
hist(carb_diabetes$pm_2016, breaks=32)
hist(carb_diabetes$pm_2015, breaks=32)
hist(carb_diabetes$pm_2014, breaks=32)
hist(carb_diabetes$poverty_14)
hist(carb_diabetes$poverty_15)
hist(carb_diabetes$poverty_16)
hist(carb_diabetes$poverty_17)
hist(carb_diabetes$unemployment_14)
hist(carb_diabetes$unemployment_15)
hist(carb_diabetes$unemployment_16)
hist(carb_diabetes$unemployment_17)

```